    \chapter{Graphics} \label{appgra}

    There are two aspects of Display functionality in current implementation.

    \begin{enumerate}

        \item
        Application that provides raw data
        \item
        Graphics routines that display this raw data.

    \end{enumerate}

    We will take a look at where these above mentioned aspects stand in
    case of each mode of display.


    Programmers Hierarchical Interactive Graphics System(PHIGS) have been used
    to perform the second part. Here is brief introduction to what PHIGS is.
    In recent years,PHIGS has been championed by producers and consumers alike
    as the
    state of the art solution to the perennial problem of the CAD applications
    developer : to find a standard device independent platform supporting
    interactive 3D computer graphics and application modeling.~\cite{Howard}

    PHIGS works on a database called Centralized structure store ( CSS). The
    application uses graphics workstation ( which is abstracted Display driver)
    to display and communicate with the model.This is similar to Document View
    architecture where database and display are separated.  After defining the
    model in terms of structures ,you can ask PHIGS to display all/ some part
    of the network of structures in specified view coordinate system.Sun PHIGS
    which is an extension of PHIGS called PHIGS PLUS( PHIGS Plus Lumie`re Und
    Shading).


    Despite PHIGS having been in widespread use for several years, a recent
    survey shows that, while there are many sources that address the
    functionality and technical implementation issues, remarkably little
    information is yet available reporting experience of using PHIGS for solving
    real problems.~\cite{Howard}


    \section{Advantages of PHIGS }

    \begin{enumerate}

    \item
    Its a higher level graphics library. It provides basic objects and
    associated functionality with help of which you build your model.
    Internal display procedure is abstracted from the user so that
    almost no lower level routines are to be written by the user.

    \item
    The Database ( CSS) and viewing is separated giving capability of
    selecting different parts of database to view at same or different
    specifications.

    \item
    PHIGS abstracts display drivers, plotters, printers under one category
    of Workstation making it advantageous in portability in terms of
    output. It allows you to write applications that are almost independent
    of hardware, operating system or graphics drivers.

    \item
    Its networked. You can produce pictures simultaneously on a whole
    network of machines, with different picture on each.

    \item
    Easy to connect to almost all Windows Graphical User Interface libraries

    \end{enumerate}

    \section{Limitations of PHIGS}

    \begin{enumerate}

    \item
    Its poor at animation.
    \item
    Lacks ray tracing or radiocity, texture mapping.
    \item
    Its not very flexible in terms of extending the capabilities.
    \item
    Need to use advanced constructs to control the traversal of network
        there by controlling the final display.

    \end{enumerate}

