% ----------------------------------------------------------------------------------------------------
\chapter{Introduction} \label{ch:Introduction}
\myquote{Many things, difficult to design, prove easy to performance.}{Samuel Johnson}
\input{Introduction_Overall_2017_thesis}

% ----------------------------------------------------------------------------------------------------
\chapter{Literature Survey} \label{ch:Survey}
\myquote{If I have seen further than others, it is by standing upon the shoulders of giants.}{Isaac Newton}
\input{LitSurvey_Overall_2017_thesis}

% ----------------------------------------------------------------------------------------------------
\chapter{MidAS - A System for Generating Midsurface for Sheet Metal Feature-based CAD Model}  \label{ch:Proposal}
\myquote{The best solutions are often simple, yet unexpected.}{Julian Casablancas}
\input{Body_Overall_2017_thesis}

% ----------------------------------------------------------------------------------------------------
\chapter{Defeaturing of Sheet Metal Feature-based CAD Model} \label{ch:Defeaturing}
\myquote{Everything Should Be Made as Simple as Possible, But Not Simpler.}{Albert Einstein}
\input{IntroductionLitSurvey_Defeaturing_2017_thesis}
\input{Body_Defeaturing_2017_thesis}
\input{Results_Defeaturing_2017_thesis}
\input{Conclusion_Defeaturing_2017_thesis}

%----------------------------------------------------------------------------------------------------
\chapter{Transformation of CAD Features to Generalized Feature Representation} \label{ch:Abstraction}
\myquote{Two elements are needed to form a truth - a fact and an abstraction.}{Remy de Gourmont}
\input{IntroductionLitSurvey_ABLE_2017_thesis}
\input{Body_ABLE_2017_thesis}
\input{Results_ABLE_2017_thesis}
\input{Conclusion_ABLE_2017_thesis}

% ----------------------------------------------------------------------------------------------------
\chapter{Generation of Midsurface from Generalized Sheet Metal CAD Part Model} \label{ch:Midsurface}
\myquote{Nothing is particularly hard if you divide it into small jobs.}{Henry Ford}
\input{IntroductionLitSurvey_MidsurfCellJoin_2017_thesis}
\input{Body_MidsurfCellJoin_2017_thesis}


%----------------------------------------------------------------------------------------------------
\chapter{Validation of Generated Midsurface} \label{ch:Validation}
\myquote{In God we trust. All others must bring data.}{W. Edwards Deming}
\input{IntroductionLitSurvey_TopoVal_2017_thesis}
\input{Body_TopoVal_2017_thesis}
\input{Conclusion_TopoVal_2017_thesis}


%----------------------------------------------------------------------------------------------------
\chapter{Case-studies} \label{ch:Testing}
\myquote{Program testing can be used to show the presence of bugs, but never to show their absence!}{Edsger Dijkstra}
\input{Results_Overall_2017_thesis}

%----------------------------------------------------------------------------------------------------
\chapter{Conclusions} \label{ch:Conclusions}
\myquote{To succeed, jump as quickly at opportunities as you do at conclusions.}{Benjamin Franklin}
\input{Conclusion_Overall_2017_thesis}

%---------------------------------------------------------------------------------------------------

