\begin{abstract}

Quest for describing shapes in a concise but expressive manner is going on for ages. Algebraic equations, Shape Grammars, Graph Grammars (collectively called as {\em Spatial Grammars}) are such attempts which have progressed in certain fields but are not ubiquitous. Use of shapes in Computer-Aided-Design (CAD) applications, which are popular primarily in Mechanical Design and Architecture, is to document already conceived design. Main focus of Spatial Grammars has been on generative-evolutionary-exploratory designing. But these capabilities, due to lack of easy-to-use tools and complexity have not found way into mainstream CAD applications. In this paper, Spatial Grammars are leveraged not for their generative capabilities but for their concise and neutral way of representing shapes. 

{\em Design-by-Features} is a popular approach in commercial CAD applications where, {\em features} (called {\em form features} in the context of geometric modeling), carry information about shapes as well as functionality and are presented with a vocabulary of the application. Diversity of {\em feature} schema creates problem in interoperability of CAD data and in development of algorithms portable across various systems. 

We propose a novel representation which has potential to address these problems. It demonstrates how {\em primitives} and widely used {\em form features} can be formulated in terms of succinct notation and proves its efficacy by developing an application-specific feature, called {\em Midsurface}.


\end{abstract}

%%% The ``CRCatlist'' environment defines one or more ACM ``Computing Review''
%%% (or ``CR'') categories, used for indexing your work. For more information
%%% on CR categories, please see http://www.acm.org/class/1998.

\begin{CRcatlist}
  \CRcat{I.3.5}{Computer Graphics}{Computational Geometry and Object Modeling}{Curve, surface, solid, and object representations}
  \CRcat{I.3.5}{Computer Graphics}{Computational Geometry and Object Modeling}{Hierarchy and geometric transformations}
\end{CRcatlist}

%%% The ``\keywordlist'' prints out the user-defined keywords.

\keywordlist

%%% If you are preparing a paper to be presented in the Technical Papers
%%% program at one of our annual flagship events (and, therefore, using 
%%% the ``tog'' parameter to the ``\documentclass'' command), the 
%%% ``\TOGlinkslist'' command prints out the list of hyperlinked icons.
%%% If you are using any other parameter to the ``\documentclass'' command
%%% this command does absolutely nothing.

%\TOGlinkslist

%%% The ``\copyrightspace'' command will leave clear an amount of space
%%% at the bottom of the left-hand column on the first page of your paper,
%%% according to the parameter used in the ``\documentclass'' command.

\copyrightspace