\section{Conclusion}

%Simplification by removing the irrelevant data, decomposition to reduce complexity of the domain, and abstraction/generalization to devise a generic logic, have been core themes of this work to compute a well-connected midsurface.

Computation of midsurface is one of the most popular \replaced{and important idealization}{ simplification} techniques for CAE analysis of  thin-walled models. Study of the existing techniques revealed critical insights into the problems of the  midsurface results (gaps, overlaps, lack of isomorphism, etc.), such as failures in the face-pair detection and interactions. \deleted[remark={Author: Removed for brevity}]{Interactions were studied to conclude that the cellular decomposition can be used to develop a uniform logic for joining the midsurface patches.}

\deleted[remark={Author: Removed for brevity}]{In the proposed approach, a feature-based  CAD model of thin-walled solid is simplified first by defeaturing techniques to result into ``gross shape'' which is found to reduce failures in the  downstream process. The remaining features are then converted to their equivalent generic form of Sweep/Loft.  Model is decomposed so that computing midsurface patches from each sub-volume, as well as connecting them becomes far easier.  Thus, the proposed methodology scores over existing approaches not only in terms of simplifying the complexities to a great extent, but also being applicable over a wide variety of geometries and connection types. } % (Table  \ref{tab:defeat_test}). 

All the sub-processes used in this work leverage feature-information effectively, thereby introducing a new way of \textbf{FSAD} (Feature-based, Simplification, Abstraction, Decomposition)  methodology to CAD algorithms.

\added[remark={Reviewer 1(2): . It is suggested that they summarize their contributions early in the paper.  Reviewer 2(2):  what is the research contribution or novelty of this work.}]{The superiority of the proposed approach is the manner in which it has abstracted both the sub-problems. Following are the salient contributions of this approach with respect to past ones:}
\begin{itemize}[noitemsep,topsep=2pt,parsep=2pt,partopsep=2pt]
\item \textbf{Simplification}: Domain specific taxonomies can be introduced for defeaturing to suit particular applications. The generic Remnant feature approach is far accurate than full-feature-parameters, for detection of suppressible features.
\item \textbf{Abstraction}: Instead of devising algorithms of plethora of feature shapes, a singular Loft based feature-transformation is far more effective as well as maintainable. Any new introduction of a domain specific feature, just needs one-time transformation rule, rest of the midsurface algorithm works without any changes.
\item \textbf{Decomposition}: Divide-and-conquer methodology, reduces the complexity of the problem. Cells, in this case, the loft primitives, are easy to create midsurface patches of and the graph structure of the cells gives accurate information needed to address midsurface connectivity issues.
\end{itemize}



%\begin{table}[!htb]
%  \centering 
%\resizebox{0.8\linewidth}{!}{ 
%\begin{tabular}[htp]{@{} p{0.15\linewidth} p{0.22\linewidth}  p{0.22\linewidth} p{0.22\linewidth} p{0.22\linewidth}@{}}
%\toprule
%\textbf{Researcher}  &	\textbf{Method} &	 \textbf{Shortcomings}  &	 \textbf{Our Approach}\\ \midrule
%\textbf{Chong et al.} \cite{Chong2004}  & 
%Uses concave edge decomposition. Midcurves by collapsing edge pairs. If they form a loop, creates a midsurface patch. & 
%Hard-coded inequalities/values to detect edge-pairs. Connection logic is not generic and comprehensive. &
%A generic treatment for the computation of midcurves, midsurface patches and their connections.
%\\ \midrule
% \textbf{Boussuge et al.} \cite{Boussuge2014}  & 
% Generative decomposition. Recognizes Extrudes of each sub-volume. Creates midsurface patches in each sub-volume and connects them together. &
% 
% \begin{itemize}[noitemsep,nosep,leftmargin=*]
%\item No fillets/chamfers.
%\item Only Additive cells.
%\item Only Extrudes with Analytical surfaces.
%\item Expensive MAT to detect thin profiles.
%\item Works only on Parallel and Orthogonal connections.
%\end{itemize}
%&
%\begin{itemize}[noitemsep,nosep,leftmargin=*]
%\item No such restriction.
%\item Re-inserts -ve cells.
%\item Generic Sweep extend-able to Loft.
%\item Simple rules of size of profile/guide.
%\item Generic logic for any numbers/types of connections.
%\end{itemize}
%
%\\ \midrule
%
%\end{tabular}
%}
% \caption{Comparison with Other Methods}
%  \label{tab:defeat_test}
%\end{table}


Although individual functionalities such as defeaturing, abstraction and decomposition processes may show certain shortcomings, but overall, the proposed approach seems to work well and is able to compute a well-connected midsurface in a robust, definitive and generic manner, with minimal failures.  

%The superiority of the proposed approach is in the manner in which it has abstracted both the sub-problems, i.e., computation of midsurface patches and resolving interactions amongst them. No heuristic rules based on specific surface-types or connection configurations are used, making the whole process generic and adaptable in a wide variety of configurations.


